---
title: "Social Network Analysis on Disney Films"
author: "Kathleen Yoojin Jeong"
date: "09/30/2022"
output: html_document
---

```{r, warning=FALSE}
suppressMessages({
  library(stringr)
  library(tidyverse)
  library(gdata)
  library(base)
  library(scales)
  library(RColorBrewer)
  library(igraph)
  library(qgraph)
  library(ggpubr)
  library(ggrepel)
  library(ggpattern)
  library(purrr)
  library(ergm)
  library(intergraph)
  library(netplot)
  library(broom)
  library(pander)
  library(gtools)
})
```


__Cleaned dataset Format__

* columns : `from`, `text`, `directed`, `to` 
* rows : each dialogue 

# I. Define functions 

__1. Open csv dataset and remove blank spaces__

```{r}
# Open csv file and add n_words column  
load_and_n_words <- function(movie_name){
  df_name <- paste0('directed-datasets/', movie_name, '-cl-directed.csv')
  df <- read.csv(df_name, na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8")
  
  for (i in 1:nrow(df)){
    df$nwords[i] <- str_count(df$text[i], '\\w+')
  }
  return(df)
}

# Remove leading and trailing blanks in name and text 
remove_empty_space2 <- function(df){
  df$from <- trim(df$from)
  df$text <- trim(df$text)
  df$directed <- trim(df$directed)
  df$to <- trim(df$to)  
  
  return(df)
}
```


__2. Compute number of words__

* For each directed dialogue
* For each character (i.e., both directed and not directed)

```{r}
# 1) Create a df with number of words of ONLY DIRECTED dialogues 
create_df_directed <- function(df){
  df_directed <- df %>% 
    filter(df$directed == 1) %>% 
    group_by(from, to) %>% 
    summarize(weight = sum(nwords))
  
  df_directed <- merge(df_directed, df_0_all_movies[,c("from", "to", "movie")], by = c("from", "to"), all.x = TRUE)
  df_directed <- df_directed[!duplicated(df_directed), ]
  row.names(df_directed) <- 1:nrow(df_directed)
  
  return(df_directed)
}

# 2) Create a df with number of words of ALL dialogues 
create_df_both <- function(df){
  df_both <- df %>% 
    group_by(from) %>% 
    summarize(n_words_total = sum(nwords))

  row.names(df_both) <- 1:nrow(df_both)
  
  return(df_both)
}
```

__3. Create `igraph` object__

 `###`라고 표시한 부분을 수정했음 
```{r}
create_igraph <- function(df_movie){
  # Compute number of words 
  # for (1) directed dialogues and (2) both directed and undirected 
  my_df_dir <- df_movie %>% 
    create_df_directed()
  my_df_both <- df_movie %>% 
    create_df_both()
  
  # Create character matrix (to create adjacency matrix)
  chars <- my_df_both$from
  from <- c()
  to <- c()
  
  for (i in 1:length(chars)){
    from <- append(from, rep(chars[i], times = length(chars)))
    }
  
  to <- append(to, rep(chars, times = length(chars)))
  my_char_mat <- data.frame(from, to) # my char matrix
  remove(chars, from, to) # remove unnecessary objects 
  
  ## Merge n_words_dialogue to each directed dialogue 
  my_char_mat <- merge(my_char_mat, 
                       my_df_dir[,c("from", "to", "weight")],  
                       by = c("from", "to"), 
                       all.x = TRUE)
  ## Remove duplicates
  my_char_mat <- my_char_mat[!duplicated(my_char_mat), ]
  
  ## Merge gender to my_df_both 
  named_char <- read.csv('0-named-char.csv', na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8") %>% 
    rename(from = X.U.FEFF.from)
  my_df_both <- merge(my_df_both, named_char[,c("from", "gender")], by = "from", all.x = TRUE)
  
  
  # Create graph object 
  v <- unique(c(my_char_mat[,1], 
                my_char_mat[,2]))
  v <- na.omit(v)
  e <- na.omit(my_char_mat)
  g <- graph.data.frame(e, vertices = v, directed = T)
  
  # Add attributes 
  V(g)$n_words_total <- my_df_both$n_words_total
  V(g)$gender <- my_df_both$gender

  return(g)
  } # end of function definition 
```

__3.1 Visualize character network__
```{r}
# 모든 영화를 한번에 plot 하기 - 얘만하면 됨 

plot_char_net_rm_isolates <- function(my_network, my_movie){
  # remove isolates
  my_network <- delete_vertices(my_network, degree(my_network) == 0)
  # layout 
  e <- get.edgelist(my_network, names=FALSE)

  if (gorder(my_network) < 18){
    my_layout <- qgraph.layout.fruchtermanreingold(e, vcount=vcount(my_network),
                                                 area=2.2*(vcount(my_network)^1.15), repulse.rad=(vcount(my_network)^1))    
  } else if (gorder(my_network) < 35){
    my_layout <- qgraph.layout.fruchtermanreingold(e, vcount=vcount(my_network),
                                                 area=2.25*(vcount(my_network)^2.1), repulse.rad=(vcount(my_network)^1.5))   
  } else {
    my_layout <- qgraph.layout.fruchtermanreingold(e, vcount=vcount(my_network),
                                                 area=3*(vcount(my_network)^2.1), repulse.rad=(vcount(my_network)^1.5))   
  }

  # plot 
  plot.igraph(my_network,
              vertex.size = rescale(V(my_network)$n_words_total, c(3, 25)),
              vertex.color = adjustcolor(ifelse(V(my_network)$gender == 0, "#009E73", 
                      ifelse(V(my_network)$gender == 1, "#E69F00", "#999999")),
                      alpha.f = .6),
              vertex.label = ifelse(V(my_network)$name %in% named_char_major$from, V(my_network)$name, ""),
              vertex.label.cex = rescale(V(my_network)$n_words_total, c(0.8, 1.6)),
              vertex.label.family = "Cambria",
              vertex.label.font = 2, # bold text 
              vertex.label.color = "black",
              edge.width = rescale(E(my_network)$weight, c(0.05, 10)), ###
              edge.arrow.size = 0.45,
              edge.color = adjustcolor("azure3", alpha.f = .6),
              edge.curved = 0.25, 
              layout = my_layout,
              main = paste0("Character Network for <", my_movie, ">")
              )
  
  legend("topright", legend = c("Woman", "Man"), 
         inset=c(0.05, 0), cex = 0.9, pch = 19, 
         col = c("#009E73", "#E69F00"), title = "Gender" 
       )
}

```

__4. Compute centrality__
```{r}
# Compute centrality 
compute_centrality <- function(my_network, my_movie){
  # In- and out-degree centrality 
  id <- degree(my_network, mode="in")
  od <- degree(my_network, mode = "out")
  # Betweenness
  bet <- betweenness(my_network, weights = E(my_network)$weight)
  # Closeness
  clo <- closeness(my_network, weights = E(my_network)$weight)
  
  # n_words_total
  n_words_total <- V(my_network)$n_words_total
  
  my_df <- data.frame(from=names(id), id=id, od=od, bet=bet, clo=clo, n_words = n_words_total, row.names=NULL)
  my_df$movie <- my_movie
  
  remove(id, od, bet, clo)
  
  return(my_df)
}
```


# II. Apply 

## Load each transcript (`xxxx-cl-directed.csv`)

```{r}
# movie list in alphabetical order 
movie_list <- c("aladdin19", "aladdin", "beauty17", "beauty", "brave", "cind", "frog", "frozen2", "frozen", 
                "incredibles1", "incredibles2", "inside", "mermaid2", "mermaid", "moana", "mulan", "poca", "raya", 
                "sleeping", "snow", "tangled", "toystory1", "toystory2", "toystory3", "toystory4")

for (i in 1:length(movie_list)){
  
  tmp <- load_and_n_words(movie_list[i])
  tmp$movie <- movie_list[i]
  
  assign(paste0("df_3_", movie_list[i]), tmp)
}
remove(tmp)
```


## Merge all preprocessed data of all films 

```{r}
# Merge all preprocessed data of all films 

# movie list in release year order 
movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya", 
                "toystory1", "toystory2", "toystory3", "toystory4", 
                "incredibles1", "incredibles2", "inside")
df_0_all_movies <- data.frame()
for (i in 1:length(movie_list)){
  df_tmp <- load_and_n_words(movie_list[i])
  df_tmp$movie <- movie_list[i]
  df_0_all_movies <- rbind(df_0_all_movies, df_tmp) %>% 
    remove_empty_space2
}
remove(df_tmp)
```


# 2. Calculate number of words 

```{r}
# For each directed dialogue
df_1_dir <- create_df_directed(df_0_all_movies)

# For each character 
df_1_both <- create_df_both(df_0_all_movies)

# Get all unique characters who interacted with another (either from or to)
all_char <- append(df_1_dir$from, df_1_dir$to) %>% unique()
df_1_char <- data.frame(from = all_char)
df_1_char <- merge(df_1_char, df_1_dir[,c("from", "movie")], by = "from") %>% unique() %>% arrange(movie)

# Save to csv 
write.csv(df_1_char,"0_unique_char.csv", row.names = F, fileEncoding = 'utf8')
```


# 3. Create igraph object 

```{r, warning=FALSE, message=FALSE}
# 모든 영화를 한번에 graph 만들기 
# Apply 
movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya", 
                "toystory1", "toystory2", "toystory3", "toystory4", 
                "incredibles1", "incredibles2", "inside", "nemo")

for (i in 1:length(movie_list)){
  tmp <- load_and_n_words(movie_list[i])
  tmp$movie <- movie_list[i]
  
  my_net <- create_igraph(tmp)
  
  assign(paste0("net_", movie_list[i]), my_net)
  remove(tmp, my_net)
}
```


## 3.1 Visualize character network 


픽사 영화들은 노드 간 거리를 좀 두자  

```{r, fig.height=8, fig.width=8, warning = FALSE, message = FALSE}
named_char_major <-  read.csv('0-named-char-major2.csv', na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8") %>%
  rename(from = X.U.FEFF.from)

movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya",
                "toystory1", "toystory2", "toystory3", "toystory4",
                "incredibles1", "incredibles2", "inside", "nemo")
movie_name_list <- c("Snow White and the Seven Dwarfs", "Cinderella", "Sleeping Beauty", "Litte Mermaid", "Little Mermaid 2",
                     "Beauty and the Beast", "Beauty and the Beast (2017)", "Aladdin", "Aladdin (2019)",
                     "Pocahontas", "Mulan", "Princess and the Frog", "Tangled", "Brave", "Frozen", "Frozen 2", "Moana", "Raya and the Last Dragon",
                     "Toy Story 1", "Toy Story 2", "Toy Story 3", "Toy Story 4",
                     "Incredibles", "Incredibles 2", "Inside Out", "Finding Nemo")

plot_list = list()
for (i in 1:length(movie_list)){
  # load each movie 
  tmp <- load_and_n_words(movie_list[i])
  tmp$movie <- movie_list[i]
  
  # create network
  my_net <- create_igraph(tmp)
  # save network object
  assign(paste0("net_", movie_list[i]), my_net)   
  
  # plot
  my_plot <- plot_char_net_rm_isolates(my_net, movie_name_list[i])
  my_plot
  
  # save plots to a list 
  plot_list[[i]] <- my_plot

  remove(tmp, my_net, my_plot)
}

```



# 4. Compute centrality 

```{r, warning = FALSE}
# Apply 
movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya", 
                "toystory1", "toystory2", "toystory3", "toystory4", 
                "incredibles1", "incredibles2", "inside", "nemo")
year_list <- c(1937, 1950, 1959, 1989, 2000, 1991, 2017, 1992, 2019, 
               1995, 1998, 2009, 2010, 2012, 2013, 2019, 2016, 2021,
               1995, 1999, 2010, 2019, 
               2004, 2018, 2015, 2003)

df_2_centrality <- data.frame()
for (i in 1:length(movie_list)){
  tmp <- load_and_n_words(movie_list[i])
  tmp$movie <- movie_list[i]
  
  my_net <- create_igraph(tmp)
  my_centrality <- compute_centrality(my_net, movie_list[i])
  
  df_2_centrality <- rbind(df_2_centrality, my_centrality)
  remove(tmp, my_net)
}

# Get character names 
named_char <- read.csv('0-named-char.csv', na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8") %>% 
  rename(from = X.U.FEFF.from)
char_names <- named_char$from

# Get years 
year <- read.csv('0-year.csv', na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8") %>% 
  rename(movie = X.U.FEFF.movie)

# Merge char names and year 
df_2_centrality <- merge(df_2_centrality, named_char[,c("from", "gender")], by = "from", all.x = TRUE) 

for (i in 1:length(movie_list)){
  df_2_centrality$year[df_2_centrality$movie == movie_list[i]] <- year_list[i]
}
df_2_centrality$year <- as.factor(df_2_centrality$year)

remove(id, od, bet, clo)
```

# Visualize centrality 

## 한 영화씩 


## Movies with sequels 

Toy Story의 경우 line plot으로 각 캐릭터의 centrality가 1-4편으로 갈수록 어떻게 바뀌는지 봐야할듯 

## All movies 

`df_2_centrality` 만드는 코드 

```{r, fig.width=10, fig.height=5}
# Number of words - PIXAR 
df <- df_2_centrality %>% 
  drop_na(gender) %>% 
  group_by(movie) %>% 
  mutate(n_words_perc = round(n_words/sum(n_words)*100, 2)) %>% 
  arrange(year, from)

df_2_centrality_cl <- df 

df$pixar <- ifelse(grepl("toystory", df$movie), "Pixar", 
                   ifelse(grepl("incredibles", df$movie), "Pixar", "DisneyPrincess"))
```



#### 1-1. 각 영화당 값 1개로 

여성 1인당 말한 정도 and 남성 1인당 말한 정도 (`perc_per`)

```{r, fig.height=5.5, fig.width=8}
df_4_movie_name <- read.csv('0_movie_name.csv', na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8") %>% 
  rename(movie = X.U.FEFF.movie) 

# n_words_total aggregated by gender 
df_2_perc_words <- df_2_centrality_cl %>%
  group_by(movie, gender) %>% 
  summarize(perc_subtotal = sum(n_words_perc), 
            pop_subtotal = n()) %>% 
  mutate(perc_per = perc_subtotal/pop_subtotal)

df_2_perc_words <- merge(df_2_perc_words, 
                         df_2_centrality_cl[,c("movie", "year", "gender")], 
                         by = c("movie", "gender"), 
                         all.x = TRUE) %>% unique() 
df_2_perc_words <- merge(df_2_perc_words, 
                         df_4_movie_name[,c("movie", "company", "movie_name")], 
                         by = c("movie"), 
                         all.x = TRUE) 
df <- df_2_perc_words
# df

df_tmp <- df %>% filter(gender == 0)


# Subtotal for all women  
ggplot(df, 
       aes(x=reorder(movie_name, as.numeric(year)), y=perc_subtotal, group = as.factor(gender)), label = df_tmp$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company") + 
  ylab("% of number of words spoken") + 
  xlab("Film") + 
  ggtitle("How much do women characters talk?") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size=14, face="bold")) 
remove(df_tmp)

# Per person for each gender 
ggplot(df, aes(x=reorder(movie_name, as.numeric(year)), y=perc_per, group = as.factor(gender)), label = df$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company", labels = c("Disney Princess", "Pixar")) +
  ylab("% of number of words spoken (per person)") + 
  xlab("Film") + 
  ggtitle("How much do each gender talk per one person?") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size=14, face="bold")) 
```

```{r, fig.height=7, fig.width=8}
df <- df_2_perc_words
df_tmp <- df %>% filter(gender == 1) %>% 
  mutate(men_talk = perc_subtotal)

df <- merge(df, df_tmp[,c("movie_name", "men_talk")], by = "movie_name", all.x = TRUE)
df

# Subtotal for all women  
ggplot(df, 
       aes(x=reorder(movie_name, as.numeric(men_talk)), 
           y=perc_subtotal, 
           fill = as.factor(gender),
           pattern= company)) +
  geom_bar_pattern(position = "fill", stat = "identity", width = 0.5,
                   color = "black", 
                   pattern_fill = "darkgrey",
                   pattern_angle = 45,
                   pattern_density = 0.03,
                   pattern_spacing = 0.04,
                   pattern_key_scale_factor = 0.6,
                   pattern_alpha = 0.6,
                   alpha = 0.7) + 
  # geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  # geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +
  # scale_fill_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_fill_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +
  # scale_shape_manual(values=c(16, 3), name = "Company") + 
  scale_pattern_manual(values = c(DisneyPrincess = "none", Pixar = "stripe"), name = "Company",
                       labels = c("Disney Princess", "Pixar")) + 
  ylab("Percent of number of words spoken") + 
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Film") + 
  ggtitle("How much do women characters talk?") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size=14, face="bold")) +
  coord_flip()
```
* https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
* 

#### sequels and live-actions 
```{r}
# centrality aggregated by gender 
df_2_cent_agg <- df_2_centrality_cl %>%
  group_by(movie, gender) %>% 
  summarize(id_subtotal = sum(id),
            od_subtotal = sum(od),
            bet_subtotal = sum(bet), 
            clo_subtotal = sum(clo),
            pop_subtotal = n()) %>% 
  mutate(id_avg = id_subtotal/pop_subtotal,
         od_avg = od_subtotal/pop_subtotal, 
         bet_avg = bet_subtotal/pop_subtotal,
         clo_avg = clo_subtotal/pop_subtotal)

df_2_cent_agg <- merge(df_2_cent_agg, 
                         df_2_centrality_cl[,c("movie", "year", "gender")], 
                         by = c("movie", "gender"), 
                         all.x = TRUE) %>% unique() 
df_2_cent_agg <- merge(df_2_cent_agg, 
                         df_4_movie_name[,c("movie", "company", "movie_name")], 
                         by = c("movie"), 
                         all.x = TRUE) 
df <- df_2_cent_agg

df

# centrality measures 

centrality_lineplot <- function(y, ylab, title, subtitle){
  p <- ggplot(df, 
       aes(x=reorder(movie_name, as.numeric(year)), y=y, group = as.factor(gender)), label = df$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +

  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +  
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company") + 
  ylab("") + 
  xlab("Film") + 
  labs(title = title,
       subtitle = subtitle) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size = 13, face="bold")) 
  
  return(p)
}
```

```{r, fig.width=9, fig.height=5}
centrality_lineplot(df$id_subtotal, "In-degree centrality (subtotal)", "Are women spoken to more characters than men?", "Indegree centrality (subtotal)")
centrality_lineplot(df$id_avg, "In-degree centrality (average)", "Is one woman spoken to more characters than one man?", "Indegree centrality (average)")
centrality_lineplot(df$od_subtotal, "Out-degree centrality (subtotal)", "Do women speak to more characters than men?", "Outdegree centrality (subtotal)")
centrality_lineplot(df$od_avg, "Out-degree centrality (average)", "Does one woman speak to more characters than one man?", "Outdegree centrality (average)")
centrality_lineplot(df$bet_subtotal, "Betweenness centrality (subtotal)", "Are women acting like a bridge more than men?", "Betweenness centrality (subtotal)")
centrality_lineplot(df$bet_avg, "Betweenness centrality (average)", "Does one woman act like a bridge more than one man?", "Betweenness centrality (average)")
centrality_lineplot(df$clo_subtotal, "Closeness centrality (subtotal)", "Are women in the center of the network?", "Closeness centrality (subtotal)")
centrality_lineplot(df$clo_avg, "Closeness centrality (average)", "Is one woman in the center more than one man?", "Closeness centrality (average)")
```


* https://stackoverflow.com/questions/29357612/plot-labels-at-ends-of-lines

### 2-1. sequels을 facet으로 묶어보기 


```{r}
ts <- c("toystory1", "toystory2", "toystory3", "toystory4")
inc <- c("incredibles1", "incredibles2")
mer <- c("mermaid", "mermaid2") 
ala <- c("aladdin", "aladdin19")
bea <- c("beauty", "beauty17")
fro <- c("frozen", "frozen2")

seq <- c("toystory1", "toystory2", "toystory3", "toystory4", "incredibles1", "incredibles2", 
         "mermaid", "mermaid2", "aladdin", "aladdin19", "beauty", "beauty17", "frozen", "frozen2")

df_tmp <- df_2_perc_words %>% 
  filter(movie %in% seq) %>% 
  mutate(series = ifelse(movie %in% ts, "Toy Story", 
                         ifelse(movie %in% inc, "Incredibles", 
                                ifelse(movie %in% mer, "Little Mermaid", 
                                       ifelse(movie %in% ala, "Aladdin", 
                                              ifelse(movie %in% bea, "Beauty and the Beast", "Frozen"))))))
# Subtotal for all women  
ggplot(df_tmp, 
       aes(x=movie_name, y=perc_subtotal, group = as.factor(gender)), label = df_tmp$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company") + 
  ylab("% of number of words spoken") + 
  xlab("Film") + 
  ggtitle("How much do women characters talk?") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size=14, face="bold"),
        strip.text = element_blank()) +
  facet_grid(. ~ series, scales = "free")

# Per person for each gender 
ggplot(df_tmp, 
       aes(x=movie_name, y=perc_per, group = as.factor(gender)), label = df_tmp$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company") +
  ylab("% of number of words spoken (per person)") + 
  xlab("Film") + 
  ggtitle("How much do each gender talk per one person?") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size=14, face="bold"),
        strip.text = element_blank()) +
  facet_grid(. ~ series, scales = "free")
remove(df_tmp)
```

```{r}
centrality_lineplot_seq <- function(y, ylab, title, subtitle){
  p <- ggplot(df, 
       aes(x=reorder(movie_name, as.numeric(year)), y=y, group = as.factor(gender)), label = df$movie_name) +
  geom_line(aes(color=as.factor(gender)), cex = 0.45)+
  geom_point(aes(color=as.factor(gender), shape = company), cex = 2.5) +

  scale_color_manual(values = c("#009E73", "#E69F00"), name = "Gender", labels = c("Woman", "Man")) +  
  # scale_color_discrete(name = "Gender", labels = c("Woman", "Man")) +
  scale_shape_manual(values=c(16, 3), name = "Company") + 
  ylab("") + 
  xlab("Film") + 
  labs(title = title,
       subtitle = subtitle) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size = 13, face="bold")) +
  facet_grid(. ~ series, scales = "free")
  
  return(p)
}



```


# 5. ERGM 

```{r}
# 1) Compute Degree Centrality (defined by Park et al., 2011) -> X
unique_char <- unique(df_1_dir$from)

tmp_out <-  df_1_dir%>% 
  group_by(movie, from) %>% 
  summarize(out_weight = sum(weight)) %>% 
  rename(char_name = from)
tmp_in <- df_1_dir %>% 
  group_by(movie, to) %>% 
  summarize(in_weight = sum(weight)) %>% 
  rename(char_name = to)
tmp <- merge(tmp_out, tmp_in, by = c("char_name", "movie"), all.y = TRUE) %>% 
  na.omit()
tmp$boonja <- tmp$out_weight + tmp$in_weight
tmp$multiplied <- tmp$out_weight*tmp$in_weight
boonmo <- 2*sum(tmp$multiplied)
tmp$dc <- tmp$boonja/boonmo

df_4_dc <- tmp
remove(tmp, tmp_in, tmp_out)
```


```{r, warning = FALSE, message = FALSE, include = FALSE}
# Apply 
movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya", 
                "toystory1", "toystory2", "toystory3", "toystory4", 
                "incredibles1", "incredibles2", "inside", "nemo")

mod_list <- list()

for (i in 1:length(movie_list)){
  # load data 
  tmp <- load_and_n_words(movie_list[i])
  tmp$movie <- movie_list[i]
  
  # create igraph object 
  my_net <- create_igraph(tmp)
  
  # delete vertices without gender value 
  my_net <- delete_vertices(my_net, 
                                V(my_net)[is.na(gender)])
  # compute mean and median of total number of words 
  my_mean <- mean(V(my_net)$n_words_total)
  my_median <- median(V(my_net)$n_words_total)
  
  # create node attributes
  V(my_net)$n_words_cat_mean <- ifelse(V(my_net)$n_words_total > my_mean, 
                                  "higher_mean", "lower_mean")
  V(my_net)$n_words_cat_med <- ifelse(V(my_net)$n_words_total > my_median, 
                                  "higher_med", "lower_med")
  # convert to ergm object 
  my_ergm <- asNetwork(my_net)
  
  # ergm models 
  m1 <- ergm(my_ergm ~ edges 
           + nodefactor("gender")
           + nodematch("gender"))
    
  m2 <- ergm(my_ergm ~ edges 
           + nodefactor("gender")
           + nodefactor("n_words_cat_mean")
           + nodematch("gender"))
 
  m3 <- ergm(my_ergm ~ edges 
         + nodefactor("gender")
         + nodefactor("n_words_cat_med")
         + nodematch("gender"))
 
  m4 <- ergm(my_ergm ~ edges 
         + nodefactor("gender")
         + nodecov("n_words_total")
         + nodematch("gender"))

  # Save to csv 
  m1_tidy <- tidy(m1, exponentiate = TRUE, conf.int = TRUE, conf.level = 0.95,
                  AIC = TRUE, BIC = TRUE) %>%
    mutate(signif = stars.pval(p.value))
  m2_tidy <- tidy(m2, exponentiate = TRUE, conf.int = TRUE, conf.level = 0.95,
                  AIC = TRUE, BIC = TRUE)  %>%
    mutate(signif = stars.pval(p.value))
  m3_tidy <- tidy(m3, exponentiate = TRUE, conf.int = TRUE, conf.level = 0.95,
                  AIC = TRUE, BIC = TRUE) %>%
    mutate(signif = stars.pval(p.value))
  m4_tidy <- tidy(m4, exponentiate = TRUE, conf.int = TRUE, conf.level = 0.95,
                  AIC = TRUE, BIC = TRUE) %>%
    mutate(signif = stars.pval(p.value))
  
  # save models to csv
  write.csv(m1_tidy, file.path("4_ergm_models/", paste0("m1_", movie_list[i], ".csv")))
  write.csv(m2_tidy, file.path("4_ergm_models/", paste0("m2_", movie_list[i], ".csv")))
  write.csv(m3_tidy, file.path("4_ergm_models/", paste0("m3_", movie_list[i], ".csv")))
  write.csv(m4_tidy, file.path("4_ergm_models/", paste0("m4_", movie_list[i], ".csv")))
  
  remove(tmp, my_net, my_ergm, m1, m2, m3, m4)
}
```

```{r}
files <- list.files(path = "4_ergm_models/")

df_5_ergm <- data.frame()
for (i in 1:length(files)) {
  df_tmp = read.csv(paste0("4_ergm_models/", files[i]), header = T, sep = ",")
  df_tmp = subset(df_tmp, select = -c(std.error, mcmc.error, statistic, p.value))

  df_5_ergm <- rbind(df_5_ergm, df_tmp)
}
write.csv(df_5_ergm, file.path("4_ergm_models_edited/0_ergm_models.csv"))
```


```{r}
# Apply 
movie_list <- c("snow", "cind", "sleeping", "mermaid", "mermaid2", "beauty", "beauty17", "aladdin", "aladdin19",
                "poca", "mulan", "frog", "tangled", "brave", "frozen", "frozen2", "moana", "raya", 
                "toystory1", "toystory2", "toystory3", "toystory4", 
                "incredibles1", "incredibles2", "inside", "nemo")

# rbind all films into one dataframe for each model 
df_5_m1 <- data.frame()
df_5_m2 <- data.frame()
df_5_m3 <- data.frame()
df_5_m4 <- data.frame()

for (i in 1:4){
  df_tmp1 <- data.frame()
  
  for (j in 1:length(movie_list)){
    df_tmp2 <- read.csv(paste0("4_ergm_models/m", i, "_", movie_list[j], ".csv"), 
                       na.strings=NA, header = TRUE, sep = ",", encoding = "UTF-8")
    df_tmp2$film <- ""
    df_tmp2$film[1] <- movie_list[j]
    df_tmp2 <- df_tmp2 %>% 
      select(film, everything())
    
    df_tmp1 <- rbind(df_tmp1, df_tmp2)
    
  }
  if (i == 1){
    df_5_m1 <- df_tmp1
  }
  if (i == 2){
    df_5_m2 <- df_tmp1
  }
  if (i == 3){
    df_5_m3 <- df_tmp1
  }
  if (i == 4){
    df_5_m4 <- df_tmp1
  }
}

```

